---
title: "Homework 2"
author: "Warrenkevin Henderson"
date: "9/23/2021"
output:
  html_document: default
  pdf_document: default
---

## Instructions


##### Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.


###### What is the probability that she will hear more than eight calls during any given session?

```{r}
1-dpois(8,15)
```


###### What is the probability that she will hear no calls in a session?

```{r}
dpois(0,15)
```


###### What is the probability that she will hear exactly three calls in a session?

```{r}
dpois(3,15)
```

###### Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
l = 15
x <- 0:30
probset <- dpois(x = x, lambda = l)
barplot(probset, names.arg = x, space = 0, xlab = "X", ylab = "PMF(X = x)", main = "Poisson Mass Function")
```


###### Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
rpois(104, 15)
```


###### Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
library(ggplot2)
graph <- rpois(104, 15)  
hist(graph,xlab = "No. of Calls", ylab ="Frequency", main = "Histogram of calls", xlim=c(0,25))
```
```{r}
### GaboI´m not sure if it's 0 to 25 or 0 to 30 in the x axis. 
```

